Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-04-23 sections/2homology.tex
Pushing previous changes.
until 2.3

We will now recall the $\infty$-category of disk algebras with a chosen tangential structure valued in a symmetric monoidal $\infty$-category. First, consider, following \cite{lurie_ha}, the category $\mathsf{Fin}_\ast$ whose objects are the sets $\langle n\rangle=\{\ast,1,\dots,n\}$ and whose morphisms are functions that preserve the distinguished point $\ast$. For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$. A \emph{symmetric monoidal $\infty$-category} is, after \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\in\mathscr{A}_1$ is \emph{($q$-)cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler. By (un)straightening, such a $q$ corresponds to a $\cat$-valued copresheaf $\mathscr{B}\to\cat$.} $\catC\to\mathsf{Fin}_\ast$ such that the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence $\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}$ for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$. We have abbreviated $\mathsf{N}(\mathsf{Fin}_\ast)$ to $\mathsf{Fin}_\ast$, and will mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$.

The $\infty$-category $\mathsf{Fun}^{\otimes}(\mathscr{O},\catC)\subset\mathsf{Fun}_{/\mathsf{Fin}_\ast}(\mathscr{O},\catC)$ of \emph{symmetric monoidal functors} between symmetric monoidal $\infty$-categories $\mathscr{O}$, $\catC$ is the full sub-$\infty$-category of the $\infty$-category of functors over $\mathsf{Fin}_\ast$ generated by those functors that preserve cocartesian edges. Following \cite{aft_fhstrat}, we write 
\[
    \alg{\mathscr{O}}(\mathscr{C})\coloneqq\mathsf{Fun}^{\otimes}(\mathscr{O},\mathscr{C})
\]
when $\mathscr{O}$, $\mathscr{C}$ are symmetric monoidal $\infty$-categories.

More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalisation of the properties of a symmetric monoidal $\infty$-category -- see \cite[Definition 2.1.1.10]{lurie_ha}.

@@

\begin{remark}
    The exact specification of the above $\infty$-category is not immediate, but the explanations given in \cite[def.2.0.0.7]{lurie_ha}, \cite[rem.2.1.2.19]{lurie_ha} and \cite[def.2.1.3.7]{lurie_ha} clarify the matter. A succinct explanation is also given around \cite[def.1.11]{aft_fhstrat}. Informally, the objects will be symmetric monoidal functors from $\disk(\bstr)$ to $\catC$. These are given by functors $F:\disk(\bstr) \xrightarrow{} \catC$ together with maps
    %
    \begin{equation}\label{eq:symmon_maps}
        F(U \sqcup V) \xrightarrow{\ \ \simeq \ \ } F(U) \otimes F(V),
    \end{equation}
    %
    and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \eqref{eq:symmon_maps}. A good informal explanation of this and other topics related to disk algebras can be found in the lecture notes \cite{tanaka20}.
\end{remark}

These algebras will be the algebraic input of factorization homology. To convince ourselves that this is not a huge limitation on the types of algebras that can be evaluated we have:
%
\begin{proposition}[{\cite[prop.2.12]{aft_fhstrat}}]\label{prop:framed_ndisk=En}
    Let $(\bstr \xrightarrow{} \bsc) = (* \xrightarrow{\{ \mathbb{R}^n\}} \bsc)$, namely the $\infty$-category of basics describing framed smooth $n$-manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk(\bstr)} (\catC) \simeq \alg{\mathbb{E}_n} (\catC).
    \end{equation}
    %
    Furthermore, if the $\infty$-category of basics is rather $(\bstr \xrightarrow{} \bsc) = (\mathsf{BO}(n) \xrightarrow{\{ \mathbb{R}^n\}} \bsc)$, the one describing unstructured smooth manifolds, then there is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk(\bstr)} (\catC) \simeq \alg{\mathbb{E}_n}(\catC)^{\mathsf{O}(n)},
    \end{equation}
    %
    with the (homotopy) $\mathsf{O}(n)$-invariants, where the action of $\mathsf{O}(n)$ is given by change of framing.
\end{proposition}

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[sec.5.1]{lurie_ha}. %or alternatively in appendix \Cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent. Through the work of \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

\begin{remark}
    $\disk(\bstr)$ is a symmetric monoidal $\infty$-category, however there is no way to inherit this structure to $\disk(\bstr)_{/M}$. Intuitively, this is because disjoint union cannot serve as a monoidal structure now that the disks are equipped with an embedding into a given manifold $M$; they could be such that they intersect. However, as explained in \cite[not.1.21]{aft_fhstrat}, we \emph{can} equip $\disk(\bstr)_{/M}$ with the structure of an $\infty$-operad because the symmetric monoidal unit $\emptyset$ of $\disk(\bstr)$ and $\mfld(\bstr)$ is initial. This is also the case for $\mfld(\bstr)_{/M}$ itself.

    In more details, following \cite[ex.2.5]{aft_fhstrat}, objects of $\disk(\bstr)_{/M}$ are finite sets of open embeddings of disks $(U \xhookrightarrow{} M)$. A morphism between two open embeddings $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified by an open embedding $U \xhookrightarrow{} V$ together with an isotopy between $U \xhookrightarrow{} M$ and $U \xhookrightarrow{} V \xhookrightarrow{} M$. A morphism $((U_1 \xhookrightarrow{} M), (U_2 \xhookrightarrow{} M)) \xrightarrow{} (V \xhookrightarrow{} M)$ is given by an open embedding $U_1 \sqcup U_2 \xhookrightarrow{} V$ together with two isotopies from $U_1 \xhookrightarrow{} M$ to $U_1 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$, and from $U_2 \xhookrightarrow{} M$ to $U_2 \xhookrightarrow{} U_1 \sqcup U_2 \xhookrightarrow{} M$.
\end{remark}

\begin{remark}
    The constructions of the slice category also holds, word for word, in the case of $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$. The fact that they are $\infty$-operads is also true. The key difference is what the objects and morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$. The objects are the same as before, i.e. finite sets of open embeddings into $M$. However, the morphisms now contain less information. A morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$, such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information. This also holds for higher arity morphisms too.

    That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.}.
\end{remark}

\begin{definition}
    We will refer to the $\infty$-category of algebras over the $\infty$-operads $\disk(\bstr)_{/M}$, $\disk[r](\bstr)_{/M}$, $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ in the usual way as
    %
    \begin{align}
        &\alg{\disk(\bstr)_{/M}} (\catC)& &\alg{\disk[r](\bstr)_{/M}} (\catC)& &\alg{\mfld(\bstr)_{/M}} (\catC)& &\alg{\mfld[r](\bstr)_{/M}} (\catC).&
    \end{align}
\end{definition}

@@

\begin{proposition}[{\cite[prop.2.2.4.9]{lurie_ha}}]
    Let $\mathscr{O}$ be an $\infty$-operad and let $\catC$ be a symmetric monoidal $\infty$-category. Then there is an equivalence
    %
    \begin{equation}
        \mathsf{Fun}^\otimes (\mathsf{Env}(\mathscr{O}), \catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathscr{O}} (\catC),
    \end{equation}
    %
    between the $\infty$-categories of $\mathscr{O}$-algebras in $\catC$ and symmetric monoidal functors from the symmetric monoidal envelope\footnote{A full definition of the symmetric monoidal envelope of an $\infty$-operad can be found in \cite[sec.2.2.4]{lurie_ha}. For our purposes the two important facts about $\mathsf{Env}$ are that it is a left adjoint to the forgetful functor $U: \cat^\otimes \xrightarrow{} \mathscr{O}\mathsf{p}_{\infty}$, and that the underlying $\infty$-category of $\mathsf{Env} (\mathscr{O})$ is the $\infty$-subcategory of $\mathscr{O}$ spanned by the active morphisms. Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms \cite[rem.2.2.4.6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
\end{proposition}

@@

Essentially the same argument as above, namely that over $\infty$-groupoids are contractible, also has another important consequence that we will need to make use of later:

@@

The next result is of key importance to the technical side of the theory, and will be used extensively throughout. It alone, is essentially the reason for the appearance of weakly constructible bundles in a lot of later developments.

\begin{lemma}[{\cite[lem.2.24]{aft_fhstrat}}]\label{lem:f^-1}
    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a functor of $\infty$-operads
    %
    \begin{equation}
        f^{-1}: \disk_{/N} \xrightarrow{} \mfld_{/M},
    \end{equation}
    %
    which acts on objects by sending $V \xhookrightarrow{} N$ to $f^{-1}V \xhookrightarrow{} M$.
\end{lemma}

@@

\begin{construction}\label{con:assocRL}
    Let $\mathsf{Assoc^{RL}}$ denote the multicategory\footnote{A \emph{multicategory} is like an (ordinary) category except that morphisms (now called multi-morphisms) are allowed to have multiple objects in their domain while still having only a single object in their codomain.} with three objects $R$, $A$ and $L$. To describe the multi-morphisms let $I$ be an arbitrary finite list of the objects of $\mathsf{Assoc^{RL}}$. We have:
    %
    \begin{enumerate}
        \item $\mathsf{Assoc^{RL}}(I, A)$ is empty if either $R$ or $L$ appear on the list $I$; otherwise it is given by the number of total orders of $I$.
        \item $\mathsf{Assoc^{RL}}(I, R)$ is empty if either $L$ appears on the list or $R$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $R$ is a minimum.
        \item $\mathsf{Assoc^{RL}}(I, L)$ is empty if either $R$ appears on the list or $L$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $L$ is a minimum.
    \end{enumerate}
    %
    Composition of multi-morphisms is given by concatenation. 
\end{construction}

>>>>

We will now recall the $\infty$-category of disk algebras with a chosen tangential structure valued in a symmetric monoidal $\infty$-category. First, consider, following \cite{lurie_ha}, the category $\mathsf{Fin}_\ast$ whose objects are the sets $\langle n\rangle=\{\ast,1,\dots,n\}$ and whose morphisms are functions that preserve the distinguished point $\ast$.\footnote{\label{YNAXOHZ}This category is meant to re-express the category of finite sets and \emph{partially-defined} functions over which the notion of a multicategory may be reformulated; cf.\ \cite[Construction 2.1.1.7]{lurie_ha}. A partially-defined function $f\colon\lrangle{n}^\circ\coloneqq\{1,\dots,n\}\to\lrangle{m}$ induces an ordinary function $\lrangle{n}\to\lrangle{m}$ that maps the elements on which $f$ is not defined to $\ast\in\lrangle{m}$.} For every $i\in\{1,\dots,n\}$ there is a map $\rho^i\colon\langle n\rangle\to\langle 1\rangle$ that sends $i$ to $1$ but is otherwise constant at $\ast\in\langle1\rangle$. A \emph{symmetric monoidal $\infty$-category} is, after \cite[Definition 2.0.0.7]{lurie_ha}, a cocartesian fibration\footnote{A \emph{cocartesian fibration} (\cite[Definition 01T5]{lurie_kerodon}) $q\colon\mathscr{A}\to\mathscr{B}$ between simplicial sets is one such that every edge $f\in\mathscr{A}_1$ is \emph{($q$-)cocartesian}, that is, any horn of type $\Lambda^n_0\to\mathscr{A}$, $n\geq2$, whose restriction to $\{0<1\}$ is $f$, admits a filler if its projection to $\mathscr{B}$ admits a filler. By (un)straightening, such a $q$ corresponds to a $\cat$-valued copresheaf $\mathscr{B}\to\cat$.} $p\colon\catC\to\mathsf{Fin}_\ast$ such that the maps $\rho^i\colon\langle n\rangle\to\langle 1\rangle$, $1\leq i\leq n$, induce an equivalence 
\begin{equation}\label{W1183QD}
\catC_{\langle n\rangle}\simeq(\catC_{\langle 1\rangle})^{\times n}
\end{equation} 
of $\infty$-categories for every $n\geq0$, where $\catC_{x}$ is the fiber at $x$. We have abbreviated $\mathsf{N}(\mathsf{Fin}_\ast)$ to $\mathsf{Fin}_\ast$, and will mostly abbreviate $\catC\to\mathsf{Fin}_\ast$ to $\catC$. One thinks of $\catC_{\langle n\rangle}$ as the collection of $n$-tuples of elements from the \emph{underlying $\infty$-category} $\catC_{\lrangle{1}}$, and $\rho^i$ as the $i$'th coordinate projection.

The $\infty$-category $\mathsf{Fun}^{\otimes}(\mathscr{O},\catC)\subset\mathsf{Fun}_{/\mathsf{Fin}_\ast}(\mathscr{O},\catC)$ of \emph{symmetric monoidal functors} between symmetric monoidal $\infty$-categories $\mathscr{O}$, $\catC$ is the full sub-$\infty$-category of the $\infty$-category of functors over $\mathsf{Fin}_\ast$ generated by those functors that preserve cocartesian edges. Following \cite{aft_fhstrat}, we write 
\[
    \alg{\mathscr{O}}(\mathscr{C})\coloneqq\mathsf{Fun}^{\otimes}(\mathscr{O},\mathscr{C})
\]
when $\mathscr{O}$, $\mathscr{C}$ are symmetric monoidal $\infty$-categories. This does \emph{not} coincide with the notation in \cite{lurie_ha}; nevertheless, see \Cref{NBR8AQB}. Informally, the objects will be symmetric monoidal functors from $\disk(\bstr)$ to $\catC$. These are given by functors $F:\disk(\bstr) \xrightarrow{} \catC$ together with maps
%
\begin{equation}\label{eq:symmon_maps}
    F(U \sqcup V) \xrightarrow{\ \ \simeq \ \ } F(U) \otimes F(V),
\end{equation}
%
and such that the swap in $\disk(\bstr)$, $U \sqcup V \simeq V \sqcup U$, is sent to the swap in $\catC$, $F(U) \otimes F(V) \simeq F(V) \otimes F(U)$, in a way that is compatible with the maps in \eqref{eq:symmon_maps}. A good informal explanation of this and other topics related to disk algebras can be found in the lecture notes \cite{tanaka20}.

More generally, an \emph{$\infty$-operad} is a map $\catC\to\mathsf{Fin}_\ast$ that satisfies a generalisation of the properties of a symmetric monoidal $\infty$-category: see \cite[Definition 2.1.1.10]{lurie_ha}. For these, \eqref{W1183QD} still holds: see \cite[Remark 2.1.1.14]{lurie_ha}.

@@

% \begin{remark}
%     The exact specification of the above $\infty$-category is not immediate, but the explanations given in \cite[def.2.0.0.7]{lurie_ha}, \cite[rem.2.1.2.19]{lurie_ha} and \cite[def.2.1.3.7]{lurie_ha} clarify the matter. A succinct explanation is also given around \cite[def.1.11]{aft_fhstrat}.
% \end{remark}

These algebras will be the algebraic input of factorization homology. To convince ourselves that this is not a huge limitation on the types of algebras that can be evaluated, we have, keeping in mind \Cref{16GY5V1}, the following:
%
\begin{proposition}[{\cite[Proposition 2.12]{aft_fhstrat}}]\label{prop:framed_ndisk=En}
    Let $(\bstr \xrightarrow{} \bsc) = (* \xrightarrow{\{ \mathbb{R}^n\}} \bsc)$, namely the $\infty$-category of basics describing framed smooth $n$-manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk(\bstr)} (\catC) \simeq \alg{\mathbb{E}_n} (\catC).
    \end{equation}
    %
    Furthermore, if the $\infty$-category of basics is rather $(\bstr \xrightarrow{} \bsc) = (\mathsf{BO}(n) \xrightarrow{\{ \mathbb{R}^n\}} \bsc)$, the one describing unstructured smooth manifolds, then there is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \alg{\disk(\bstr)} (\catC) \simeq \alg{\mathbb{E}_n}(\catC)^{\mathsf{O}(n)},
    \end{equation}
    %
    with the (homotopy) $\mathsf{O}(n)$-invariants, where the action of $\mathsf{O}(n)$ is given by change of framing.
\end{proposition}

\begin{remark}
    For more details on $\mathbb{E}_n$-algebras and why these algebras encompass large portions of the examples one usually cares about see \cite[§5.1]{lurie_ha}. %or alternatively in appendix \Cref{app:En_algebras}. 
    Roughly speaking, $\mathbb{E}_1$-algebras are homotopy-associative algebras and with increasing $n$ we get increasing levels of homotopy commutativity, such that the colimit $\mathbb{E}_\infty$ parametrises homotopy-commtuative algebras. Having said that, the first part of the proposition is just the classical statement that the little $n$-disks operad and the little $n$-cubes operad are equivalent. Through \cite{lurie_tqft} and \cite{scheimbauer2014}, $\mathbb{E}_n$-algebras also serve as input for constructing fully extended TQFTs by using factorization homology.
\end{remark}

@@

    While $\disk(\bstr)$ is a symmetric monoidal $\infty$-category, $\disk(\bstr)_{/M}$ need not be, since two embeddings, if their images intersect, do not lift to an embedding from the disjoint union of their domains. However, \cite[Notation 1.21]{aft_fhstrat} equips $\disk(\bstr)_{/M}$ with the structure of an $\infty$-operad. We briefly explain the idea behind the construction. It applies in the same way to $\mfld(\bstr)_{/M}$.

    Let $\iota_{1/2}\colon D_{1/2}\hookrightarrow M$ be two embeddings. A morphism over $\lrangle{2}\to\lrangle{1}$ from $(\iota_{1},\iota_2)$ to $\iota\colon D\to M$ will consist of
    \begin{enumerate}
        \item two $1$-simplices
        \[
        \begin{tikzcd}
            D_{1}\ar[dr,hook]\ar[rr,hook] && D\ar[dl,hook']\\
            & M
        \end{tikzcd},\quad
        \begin{tikzcd}
            D_{2}\ar[dr,hook]\ar[rr,hook] && D\ar[dl,hook']\\
            & M
        \end{tikzcd}
        \]
        in the slice $\disk(\bstr)_{/M}$;
        \item an embedding $ D_1\amalg D_2\hookrightarrow D$;
        \item and two isotopies -- to be explained below -- between the resulting embeddings $D_{1/2}\hookrightarrow D_{1}\amalg D_2 \hookrightarrow D$ and the previously given embeddings $D_{1/2}\hookrightarrow D$.
    \end{enumerate}

    The first piece is in $\prod_{\nu=1,2}\mathsf{Hom}_{\disk(\bstr)_{/M}}(\iota_\nu,\iota)$, and projecting from the slice gives maps $\prod_{\nu=1,2}\mathsf{Hom}_{\disk(\bstr)_{/M}}(\iota_\nu,\iota)\to \prod_{\nu=1,2}\mathsf{Hom}_{\disk(\bstr)}(D_\nu,D)$, producing the maps $D_\nu\hookrightarrow D$ mentioned in piece 3. Piece 2 is in $\disk(\bstr)$. The monoidal unit $\emptyset\in\disk(\bstr)$ is initial, so we obtain the map $\mathsf{Mul}_{\disk(\bstr)}(D_1, D_2; D)\to\prod_{\nu=1,2}\mathsf{Hom}_{\disk(\bstr)}(D_\nu,D)$ as indicated above. See \cite[Notation 2.1.1.16]{lurie_ha} for $\mathsf{Mul}$.

    Now, \cite[§2.4.3]{lurie_ha} contains a construction which associates an $\infty$-operad $\mathscr{C}^{\amalg}$ to any $\infty$-category $\mathscr{C}$ such that $\mathsf{Mul}_{\mathscr{C}^{\amalg}}(x_1\oplus\cdots\oplus x_n; y)\simeq \prod_{\nu=1}^{n}\mathsf{Hom}_{\mathscr{C}}(x_\nu,y)$. If $\mathscr{C}$ is already an $\infty$-operad with a initial unit $0\in\mathscr{C}_{\lrangle{1}}$, then there is (\cite[Lemma 1.20]{aft_fhstrat}) a canonical map of $\infty$-operads $\mathscr{C}\to(\mathscr{C}_{\lrangle{1}})^\amalg$ generalising the idea above.

    We see that piece 1 is in $(\disk(\bstr)_{/M})^{\amalg}$, piece 2 is in $\disk(\bstr)$, and piece (3) describes equivalences in $\disk(\bstr)^{\amalg}$. The full collection is thus in the homotopy pullback $\infty$-operad 
    \[
        \begin{tikzcd}
        \disk(\bstr)_{/M}\ar[r]\ar[d]\arrow[dr, phantom, "\ulcorner", very near start] & (\disk(\bstr)_{/M})^{\amalg}\ar[d]\\
        \disk(\bstr)\ar[r] & \disk(\bstr)^{\amalg}
        \end{tikzcd}.
    \]
    A representative is then the following ordinary iterated fibre product of $\infty$-operads:
    \[
        \disk(\bstr)_{/M}\coloneqq \disk(\bstr)\times_{(\disk(\bstr)^{\amalg})^{\{0\}}}\mathsf{Isom}(\disk(\bstr)^{\amalg})\times_{(\disk(\bstr)^{\amalg})^{\{1\}}}(\disk(\bstr)_{/M})^{\amalg},
    \]
    where $\mathsf{Isom}(\disk(\bstr)^{\amalg})\subset\mathsf{Ar}(\disk(\bstr)^{\amalg})=(\disk(\bstr)^{\amalg})^{\Delta[1]}$ is the full sub-$\infty$-category of the arrow $\infty$-category generated by those morphisms that are isomorphisms in the associated homotopy category, whence the isotopies mentioned in piece 3.

\begin{remark}
    Analogous statements hold for $\disk[r](\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ and the resulting $\infty$-operads. The difference is what the objects and morphisms are, say, in $\disk[r](\bstr)_{/M}$ as compared to $\disk(\bstr)_{/M}$. The objects are the same as before, i.e., finite sets of open embeddings into $M$. However, a morphism $(U \xhookrightarrow{} M) \xrightarrow{} (V \xhookrightarrow{} M)$ is specified only by open embedding $U \xhookrightarrow{} V$ such that $(U \xhookrightarrow{} M) = (U \xhookrightarrow{} V \xhookrightarrow{} M)$, and no further information. That is, a morphism in $\disk(\bstr)_{/M}$ is a diagram in $\disk (\bstr)$
    %
    \begin{equation}
        \begin{tikzcd}
            \coprod\limits_{i} U_i \arrow[rr] \arrow[rd] & & U \arrow[ld] \\
            & M, &
        \end{tikzcd}
    \end{equation}
    %
    which is homotopy commutative as explained above, while in $\disk[r](\bstr)_{/M}$ a morphism is a diagram as above that commutes on the nose.\footnote{Regarding notation, \cite{lurie_ha} introduces both the $\infty$-operad $\disk(\bstr)_{/M}$ and $\disk[r](\bstr)_{/M}$, however there they are denoted by $\mathbb{E}_M^\otimes$ and $\mathrm{N}(\mathrm{Disk}(M))^\otimes$, respectively.} 
    Similarly for higher arity-morphisms.
\end{remark}

\begin{definition}
    We will denote the $\infty$-category of algebras over the $\infty$-operads $\disk(\bstr)_{/M}$, $\disk[r](\bstr)_{/M}$, $\mfld(\bstr)_{/M}$ and $\mfld[r](\bstr)_{/M}$ by
    %
    \begin{align}
        &\alg{\disk(\bstr)_{/M}} (\catC)& &\alg{\disk[r](\bstr)_{/M}} (\catC)& &\alg{\mfld(\bstr)_{/M}} (\catC)& &\alg{\mfld[r](\bstr)_{/M}} (\catC).&
    \end{align}
    Following AFT, a map $\disk(\bstr)_{/M}\to \catC$, for instance, is in $\alg{\disk(\bstr)_/M}(\catC)$ iff, by definition, it is a map of $\infty$-operads in the sense of \cite[Definition 2.1.2.7]{lurie_ha} which maps pre-cocartesian edges to cocartesian edges. A \emph{pre-cocartesian} edge in $\disk(\bstr)_{/M}$ is an edge whose projection to $\disk(\bstr)$ is cocartesian over $\mathsf{Fin}_\ast$.
\end{definition}

@@

\begin{proposition}[{\cite[prop.2.2.4.9]{lurie_ha}}]\label{NBR8AQB}
    Let $\mathscr{O}$ be an $\infty$-operad and let $\catC$ be a symmetric monoidal $\infty$-category. Then there is an equivalence
    %
    \begin{equation}
        \mathsf{Fun}^\otimes (\mathsf{Env}(\mathscr{O}), \catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathscr{O}} (\catC),
    \end{equation}
    %
    between the $\infty$-categories of $\mathscr{O}$-algebras in $\catC$ and symmetric monoidal functors from the symmetric monoidal envelope\footnote{A full definition of the symmetric monoidal envelope of an $\infty$-operad can be found in \cite[§2.2.4]{lurie_ha}. For our purposes the two important facts about $\mathsf{Env}$ are that it is a left adjoint to the forgetful functor $U: \cat^\otimes \xrightarrow{} \mathscr{O}\mathsf{p}_{\infty}$, and that the underlying $\infty$-category of $\mathsf{Env} (\mathscr{O})$ is the $\infty$-subcategory of $\mathscr{O}$ spanned by the active morphisms. Informally, the symmetric monoidal structure of $\mathsf{Env}(\mathscr{O})$ is given by concatenating these active morphisms: see \cite[Remark 2.2.4.6]{lurie_ha}.} of $\mathscr{O}$ to $\catC$.
\end{proposition}

@@

Essentially the same argument as above, namely that over-$\infty$-groupoids are contractible, also has another important consequence that we will need to make use of later:

@@

The next result is of key importance to the technical side of the theory, and will be used extensively throughout. It alone is essentially the reason for the appearance of weakly constructible bundles in a lot of later developments.

\begin{lemma}[{\cite[Lemma 2.24]{aft_fhstrat}}]\label{lem:f^-1}
    Let $f: M \xrightarrow{} N$ be a weakly constructible bundle. There is a functor of $\infty$-operads
    %
    \begin{equation}
        f^{-1}: \disk_{/N} \xrightarrow{} \mfld_{/M},
    \end{equation}
    %
    which acts on objects by sending $V \xhookrightarrow{} N$ to $f^{-1}V \xhookrightarrow{} M$.
\end{lemma}

@@

\begin{construction}\label{con:assocRL}
    Let $\mathsf{Assoc^{RL}}$ denote the multicategory\footnote{A \emph{multicategory}, or \emph{(colored) operad}, is like an (ordinary) category except that morphisms (now called multi-morphisms) are allowed to have multiple objects in their domain while still having only a single object in their codomain. The operadic nerve of a topological or Kan-enriched multicategy is an $\infty$-operad: see \cite[Proposition 2.1.1.27]{lurie_ha}.} with three objects $R$, $A$ and $L$. To describe the multi-morphisms let $I$ be an arbitrary finite list of the objects of $\mathsf{Assoc^{RL}}$. We have:
    %
    \begin{enumerate}
        \item $\mathsf{Assoc^{RL}}(I, A)$ is empty if either $R$ or $L$ appear on the list $I$; otherwise it is given by the number of total orders of $I$.
        \item $\mathsf{Assoc^{RL}}(I, R)$ is empty if either $L$ appears on the list or $R$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $R$ is a minimum.
        \item $\mathsf{Assoc^{RL}}(I, L)$ is empty if either $R$ appears on the list or $L$ appears on the list more than once; otherwise it is given by the number of total orders of $I$ such that the possible element $L$ is a minimum.
    \end{enumerate}
    %
    Composition of multi-morphisms is given by concatenation. 
\end{construction}
